%--- Resume Template: https://www.overleaf.com/latex/templates/faangpath-simple-template/npsfpdqnxmbc ---%

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Anser Waseem} % Your name

\address{+923349863650 \\ \href{mailto:hafiz.anser.waseem@gmail.com}{hafiz.anser.waseem@gmail.com} \\ Remote (Available Worldwide)} 
\address{\href{https://www.linkedin.com/in/anserwaseem/}{linkedin.com/in/anserwaseem} \\ \href{https://github.com/anserwaseem}{github.com/anserwaseem} \\ \href{https://anserwaseem.com}{anserwaseem.com}}  %


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Accomplished Full Stack Software Engineer with 3+ years of proven expertise leading enterprise-scale projects, managing cross-functional teams, and delivering high-performance applications serving multiple health systems. Specialized in React.js, Next.js, Node.js, and TypeScript with demonstrated success in scaling development teams, architecting production-ready solutions, and integrating cutting-edge AI technologies. Seeking senior software engineering roles to drive innovation in modern web development and enterprise solutions.}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science}, FAST - NUCES  \hfill {2018 - 2022}\\
Lahore, Pakistan

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Frontend & React.js, Next.js, TypeScript, JavaScript, HTML, CSS, Tailwind CSS
\\
Backend & Node.js, Express.js, Firebase, PostgreSQL, Supabase\\
Tools \& Technologies & Electron.js, Docker, Git, Vite, Turborepo, Azure, GitHub Actions\\
AI \& Automation & Google GenAI, Custom AI Features, Chatbots, CI/CD\\
Leadership & Team Management, Code Architecture, Mentoring, Project Delivery\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Software Engineer \& Technical Lead} \hfill Aug 2023 - Present\\
Ensemble Technologies Inc. \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf{Leadership Impact:} Promoted to Technical Lead for Atlas Health project, successfully managing 3+ developers and delivering enterprise healthcare solutions serving 10+ health systems with exceptional reliability.
     \item \textbf{Cross-Platform Excellence:} Architected and deployed production-ready applications across multiple platforms: iOS shopping app using YAML EDL, complex healthcare platform in React, and desktop IDE using Electron.js with significantly improved deployment efficiency.
     \item \textbf{DevOps Innovation:} Designed and implemented comprehensive CI/CD pipeline with automated code signing, notarization for macOS/Windows, and google cloud deployment for Ensemble's low-code Studio, dramatically reducing deployment time and eliminating manual errors.
     \item \textbf{Architecture Leadership:} Spearheaded major codebase refactoring initiative in Atlas, establishing design system and reusable component widgets that substantially improved development velocity across the team.
     \item \textbf{Business Growth:} Extended multiple client contracts through exceptional delivery quality - Tin project expanded multiple times and Atlas project scope expanded significantly beyond initial timeline, resulting in team scale-up and increased revenue.
     \item \textbf{Performance Optimization:} Led ensemble-react widget library optimization initiatives, achieving substantial improvements in application responsiveness and user experience metrics.
 \end{itemize}
 
\textbf{Junior Software Developer} \hfill Jun 2022 - Aug 2023\\
Contour Software \hfill \textit{Lahore, PK}
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf{Enterprise Solutions:} Led development of serverless orchestration Azure application for large-scale data processing, dramatically improving data warehouse performance and enabling real-time analytics capabilities.
     \item \textbf{Full-Stack Development:} Architected complete Identity Management System from scratch using React, TypeScript, Material UI, and RTKQ, serving enterprise users across multiple organizations.
     \item \textbf{Backend Excellence:} Developed robust API ecosystem using .NET 6 and IdentityServer4 with comprehensive unit testing, ensuring enterprise-grade security and exceptional system reliability.
     \item \textbf{Operational Impact:} Eliminated majority of support tickets by enabling end-users to independently manage users, roles, and permissions, saving significant support team time weekly.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Easy Accounting.} {Offline-first desktop accounting system helping SMEs manage finances efficiently. Achieved high user satisfaction with complete financial management, cross-platform compatibility, and robust backup system supporting both local file system and cloud storage via Supabase. Built with Electron.js, React.js, SQLite, and Tailwind CSS.
\href{https://github.com/anserwaseem/easy-accounting/releases}{(See Desktop App)}}
\item \textbf{Automadeasy.} {Interactive tool for visual automaton design serving students and educators worldwide. Significantly reduced learning curve for Theory of Automata through intuitive visual interface. Officially adopted for teaching at FAST-NUCES University by faculty members. Built with React.js, TypeScript, and CSS. \href{https://www.automadeasy.com/}{(Try Live Demo)}}
\item \textbf{Ensemble React Toolkit.} {Core contributor to modular toolkit powering low-code applications for enterprise clients over 1.5+ years. Contributed to numerous releases with comprehensive testing suite and high code coverage. Built with React, TypeScript, Jotai, Turbo, Firebase.
\href{https://github.com/EnsembleUI/ensemble-react}{(See Contributions)}}
\item \textbf{Metadata from URL API.} {Deployed high-performance metadata extraction API on Cloudflare Workers edge network with global reach. Features intelligent caching, rate limiting, and enterprise-grade reliability. Built with Bun, Hono, and Upstash Redis.
\href{https://rapidapi.com/hafizanserwaseem/api/metadata-from-url/}{(Try it here)}}
\item \textbf{AI-Powered Portfolio Website.} {Professional showcase website featuring custom AI chatbot powered by Google Gemini API for interactive user engagement. Demonstrates modern web development excellence with responsive design and real-time AI integration. Built with Next.js, React.js, Tailwind CSS, Shadcn UI. \href{https://anserwaseem.com}{(Visit anserwaseem.com)}}
\item \textbf{Princess Dragon Slayer.} {Complete 2D platformer game showcasing advanced game mechanics, physics simulation, and user interaction design. Features comprehensive collision detection, scoring system, and engaging gameplay. Built with Godot Engine, GDScript, and Brackeys Platformer Bundle. \href{https://github.com/anserwaseem/princess-dragon-slayer}{(Experience the Game)}}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership \& Recognition} 
\begin{itemize}
    \item \textbf{Technical Leadership:} Promoted to Technical Lead at Ensemble Technologies, managing cross-functional teams and delivering enterprise healthcare solutions to multiple health systems.
    \item \textbf{Mentorship Excellence:} Actively mentor junior developers in modern React development, TypeScript best practices, and software architecture principles, contributing to strong team growth and knowledge sharing.
    \item \textbf{Project Success:} Consistently delivered projects with high quality and reliability, resulting in contract extensions and team expansion across multiple client engagements.
    \item \textbf{Innovation Driver:} Pioneered AI integration initiatives and performance optimization strategies that became standard practices across development teams.
\end{itemize}

\end{rSection}

\end{document} 